% !TEX root = ../document.tex

\begin{thebibliography}{99}

\bibitem{z1}王洪全,刘天华,欧阳承曦,姚待艳.基于星基的ADS-B系统现状及发展建议[J].通信技术,2017,50(11):2483-2489.

\bibitem{z2}王运帷. 陆基与星基ADS-B系统数据质量研究[D].中国民航大学,2018.

\bibitem{z3}袁晓晶,张军,黄智刚.空基与星基组合监视系统中的ADS-B分群算法[J].电讯技术,2007(01):82-85.

\bibitem{z4}赵嶷飞,于克非.星基广播式自动相关监视系统监视数据空中位置信息质量分析[J].科学技术与工程,2018,18(14):279-284.

\bibitem{z5}于克非. 星基ADS-B系统监视性能可用性评估[D].中国民航大学,2018.

\bibitem{z6}刘海涛,王松林,秦定本,李冬霞.星基ADS-B接收机监视容量分析[J].航空学报,2018,39(05):182-189.

\bibitem{z7}吴骏. 星载高灵敏度ADS-B接收机信号解算算法研究及实现[D].电子科技大学,2016.

\bibitem{z8}陈利虎,陈小前,赵勇.星载ADS-B接收系统及其应用[J].卫星应用,2016(03):34-40.

\bibitem{z9}刘鹏,倪育德.星基ADS-B的链路预算[J].中国科技信息,2018(14):94-97.

\bibitem{z10}杨晖 ,钟卫晋.浅谈全球星系统[J].现代通信,2003(05):3.

\bibitem{z11}邹锐.全球星系统(Globalstar)技术介绍[J].电子科技导报,1999(07):7-12.

\bibitem{z12}吴建军. 第二代铱星系统(Iridium Next)及其搭载应用概况[A]. 中国通信学会卫星通信委员会.第六届卫星通信新业务新技术学术年会论文集[C].中国通信学会卫星通信委员会:中国通信学会,2010:10.

% papers

\bibitem{e1}Ali, Syd B . System specifications for developing an Automatic Dependent Surveillance-Broadcast (ADS-B) monitoring system[J]. International Journal of Critical Infrastructure Protection, 2016:S187454821530041X.

\bibitem{e2}Delovski T , Werner K , Rawlik T , et al. ADS-B over Satellite The world’s first ADS-B receiver in Space[C]// Small Satellites Systems \& Services Symposium. DLR, 2014.

\bibitem{e2ppt}Werner K , Bredemeyer J , Delovski T . ADS-B over Satellite Global Air Traffic Surveillance from Space[C]// 2014 Tyrrhenian International Workshop on Digital Communications - Enhanced Surveillance of Aircraft and Vehicles (TIWDC/ESAV). IEEE, 2014.

\bibitem{e3}Kunzi F , Hansman R J . ADS-B Benefits to General Aviation and Barriers to Implementation[J]. Massachusetts Institute of Technology, 2011.

\bibitem{e4}Wang, Hao, "ADS-B used in Improvement of Air Traffic Control" (2015). Open Access Theses. 624.
\url{https://docs.lib.purdue.edu/open_access_theses/624}

\bibitem{e5}EASA . ADS-B and other means of surveillance implementation status[R] . 2018.

% ICAO ATTACHEMENTS

\bibitem{e6}ICAO . ADS-B SITF/15 – IP/31, UPDATE ON ADS-B ACTIVITIES IN CHINA[C]. Bankok : ICAO , 2016.

\bibitem{e7}ICAO . SEA/BOB ADS-B WG/14 – IP/3, ADS-B IMPLEMENTATION ACTIVITIES IN CHINA[C]. Bankok : ICAO , 2018.

\bibitem{e8}ICAO . ADS-B SITF/14 – IP/23 (Rev.), ADS-B IMPLEMENTATION STATUS IN INDONESIA AND DATA SHARING BETWEEN INDONESIA, AUSTRALIA AND SINGAPORE[C]. Christchurch : ICAO , 2015.

\bibitem{e9}ICAO . SEA/BOB ADS-B WG/13 – IP/09, UPDATE ON ADS-B PROJECT IN MALAYSIA[C]. Colombo : ICAO , 2017.

\bibitem{e10}ICAO . SEA/BOB ADS-B WG/12 – IP/09, UPDATE ON ADS-B IMPLEMENTATION IN THAILAND[C]. Guangzhou : ICAO , 2016.

\bibitem{e11}ICAO . SEA/BOB ADS-B WG/13 – IP/17, UPDATE ON ADS-B IMPLEMENTATION IN THE PHILIPPINES[C]. Colombo : ICAO , 2017.

% PPT & papers

\bibitem{e12}“Global Surveillance through Space-Based ADS-B”，\url{https://www.icao.int/SAM/Documents/2017-ADSB/15%20Aireon-NAM%20CAR%20SAM%20ADS-B%20WS%20v4.pdf}

\bibitem{e13}“Satellite Based ADS-B NAV CANADA”，\url{https://www.faa.gov/about/office_org/headquarters_offices/ato/service_units/systemops/ato_intl/documents/cross_polar/CPWG16/CPWG16_PPT09_Satellite_Based_ADSB_December2013.pdf}

\bibitem{e14}“Launching the Future - ITU”，\url{https://www.itu.int/en/ITU-T/Workshops-and-Seminars/ccsg/expdial/Documents/31-Globalstar.pdf}

\bibitem{e15}“from Barbee on Globalstar letterhead”，\url{https://ecfsapi.fcc.gov/file/60000975762.pdf}

\bibitem{e16}“IAA Space-Based ADS-B Projects”，\url{https://www.eurocontrol.int/sites/default/files/events/presentation/16-space-based-adsb-oloughlin.pdf}

\bibitem{e17}“GOMX-1: A Nano-satellite Mission to Demonstrate Improved Situational Awareness for Air Traffic Control”，\url{http://mstl.atl.calpoly.edu/~bklofas/Presentations/SummerWorkshop2012/Alminde_GOMX-1.pdf}

\bibitem{e18}Garcia M A , Stafford J , Minnix J , et al. Aireon space based ADS-B performance model[C]// 2015 Integrated Communication, Navigation and Surveillance Conference (ICNS). IEEE, 2015.

\bibitem{e19}Garcia M A , Dolan J , Hoag A . Aireon's initial on-orbit performance analysis of space-based ADS-B[C]// Integrated Communications, Navigation \& Surveillance Conference. IEEE, 2017.

\bibitem{e20}Noschese, Porfili, Girolamo D . ADS-B via Iridium NEXT satellites[C]// Tyrrhenian International Workshop on Digital Communications-enhanced Surveillance of Aircraft \& Vehicles. IEEE, 2011.

\bibitem{e21}Blomenhofer H , Pawlitzki A , Rosenthal P , et al. Space-based Automatic Dependent Surveillance Broadcast (ADS-B) payload for In-Orbit Demonstration[C]// Advanced Satellite Multimedia Systems Conference. IEEE, 2012.

% website

\bibitem{h1}“What is Space-Based ADS-B?”，\url{http://www.ads-b.com/space-based.htm}

\bibitem{h2}“ADS-B over Satellite”，\url{https://directory.eoportal.org/web/eoportal/satellite-missions/a/ads-b#overview}

\bibitem{h3}“Iridium satellite constellation”，\url{https://en.wikipedia.org/wiki/Iridium_satellite_constellation#Next-generation_constellation}

\bibitem{h4}“铱星系统的前世今生，通导融合的技术奇迹”，\url{http://mini.eastday.com/mobile/170228225143989.html#}

\bibitem{h5}“看‘铱星二代’和‘全球星二代’两个‘星二代’是如何当航空监视‘保镖’的？”，\url{http://www.sohu.com/a/211117337_100044418}

\bibitem{h6}“Aireon, SPACE-BASED ADS-B MAKING GLOBAL AIR TRAFFIC SURVEILLANCE A POWERFUL REALITY”，\url{https://aireon.com/}

\bibitem{h7}“WHERE IS ADS-B OUT REQUIRED?”，\url{https://www.aopa.org/go-fly/aircraft-and-ownership/ads-b/where-is-ads-b-out-required}

\bibitem{h8}“What is VDL Mode 4?”，\url{http://www.cns.se/support/faq-vdl_mode_4}

\bibitem{h9}“‘天拓三号’六颗卫星集群飞行” 能收全球航空信号，\url{http://scitech.people.com.cn/n/2015/0921/c1007-27610443.html}

\bibitem{h10}“我国试验星载航空目标自动信号在轨接收 可有效避免飞机失联”，\url{https://www.guancha.cn/Project/2015_10_12_337272.shtml}

\bibitem{h11}“Globalstar”，\url{https://en.wikipedia.org/wiki/Globalstar}

\bibitem{h12}\url{http://www.ads-b.com/news.htm}

\bibitem{h13}“GOMX 1→GATOSS”，\url{https://space.skyrocket.de/doc_sdat/gomx-1.htm}

\bibitem{h14}“GATOSS”，\url{https://earth.esa.int/web/eoportal/satellite-missions/g/gatoss#8nNiI11d4Herb}

\bibitem{h15}“GOMSpace GOMX-1”，\url{https://gomspace.com/gomx-1.aspx}

\bibitem{h16}“GOMX 3”，\url{https://space.skyrocket.de/doc_sdat/gomx-3.htm}

\bibitem{h17}“The backpack-sized satellite that can track worldwide air traffic: Esa reveals stunning image showing cubesat mission's first data”，\url{https://www.dailymail.co.uk/sciencetech/article-3528972/The-backpack-sized-satellite-track-worldwide-air-traffic-Esa-reveals-stunning-image-showing-cubesat-mission-s-data.html}

\end{thebibliography}